Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-05-03 Chapter-4/4-InteractionsInLAr.tex
s

\begin{table}[]
\centering
\begin{tabular}{|l|c|c|}
\hline
                                                        & Run-II Negative Polarity   &  Run-II Positive Polarity  \\ \hline
Events Reconstructed in Beamline &  158396  & 260810  \\ \hline
Events with Plausible Trajectory     &   147468 & 240954  \\ \hline
Candidate $\pi^-/\mu^-/e^-$            &   138481 &     N.A.   \\ \hline
Candidate $K^+$                            &    N.A       & 2837     \\ \hline
Events Surviving Pile Up Filter       &                 &              \\ \hline
Events with WC2TPC Match          &                 &              \\ \hline
Events Surviving Shower Filter      &                 &  N.A.     \\ \hline
\end{tabular}
\caption{Number of data events for Run-II Negative and Positive polarity }
\label{tab:beamlineDataSelection}
\end{table}

>>>>

\begin{table}[]
\centering
\begin{tabular}{|l|c|c|}
\hline
                                                        & Run-II Negative Polarity   &  Run-II Positive Polarity  \\ \hline
Events Reconstructed in Beamline &  158396  & 260810  \\ \hline
Events with Plausible Trajectory     &   147468 & 240954  \\ \hline
Candidate $\pi^-/\mu^-/e^-$            &   138481 &     N.A.   \\ \hline
Candidate $K^+$                            &    N.A       & 2837     \\ \hline
Events Surviving Pile Up Filter       &                 &              \\ \hline
Events with WC2TPC Match          &                 &              \\ \hline
Events Surviving Shower Filter      &   56526    &  N.A.     \\ \hline
\end{tabular}
\caption{Number of data events for Run-II Negative and Positive polarity }
\label{tab:beamlineDataSelection}
\end{table}
